---
title: "Mapping Zipcode Demographics in California for 2012"
author: "David Clark"
date: "October 12, 2015"
output: 
  html_document: 
    keep_md: yes
---

Install the required packages:

```{r}
library(devtools)
library(choroplethrZip)
library(ggplot2)
library(gridExtra)
```


Inspect the data:

```{r}
data(df_pop_zip)
head(df_pop_zip)
```

Map zipcode populations in California:

```{r}
c = ZipChoropleth$new(df_pop_zip)
c$title = "Zipcode Populations in California"
c$ggplot_polygon = geom_polygon(aes(fill = value),
                                color=NA)
c$set_zoom_zip(state_zoom = "california",
               county_zoom=NULL,
               msa_zoom=NULL,
               zip_zoom=NULL)
c$legend = "population"

c$render()

```

##Statistics for San Francisco, San Mateo and Santa Clara counties##

**County FIPS for the Peninsula:**

* San Francisco County: 06075

* San Mateo County: 06081

* Santa Clara County: 06085

```{r}
peninsula_fips = c(06075, 06081, 06085)
```

Load demographic data for zipcodes:

```{r}
data(df_zip_demographics)
colnames(df_zip_demographics)
```

###Percent Hispanic, Asian and White populations:###
Populations for San Francisco, San Mateo and Santa Clara counties.

```{r, warning=FALSE}
df_zip_demographics$value = df_zip_demographics$percent_hispanic
percentHispanic = zip_choropleth(df_zip_demographics, county_zoom=peninsula_fips, title="Percent Hispanic") +
                theme(legend.position="none")

df_zip_demographics$value = df_zip_demographics$percent_asian
percentAsian = zip_choropleth(df_zip_demographics, county_zoom=peninsula_fips, title="Percent Asian") +
                theme(legend.position="none")

df_zip_demographics$value = df_zip_demographics$percent_white
percentWhite = zip_choropleth(df_zip_demographics, county_zoom=peninsula_fips, title="Percent White") +
                theme(legend.position="none")

grid.arrange(percentHispanic, percentAsian, percentWhite, ncol=3)
```

###Median Age, Median Rent, and Per Capita Income:###
Median age, median rent, and per capita income for San Francisco, San Mateo and Santa Clara counties.

```{r, warning=FALSE}
df_zip_demographics$value = df_zip_demographics$median_age
zip_choropleth(df_zip_demographics, county_zoom=peninsula_fips, title="Median Age", legend = "age")

df_zip_demographics$value = df_zip_demographics$median_rent
zip_choropleth(df_zip_demographics, county_zoom=peninsula_fips, title="Median Rent", legend = "price ($)")

df_zip_demographics$value = df_zip_demographics$per_capita_income
zip_choropleth(df_zip_demographics, county_zoom=peninsula_fips, title="Per Capita Income", legend = "income ($)")

```

